\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-11 article.tex
Add newer cfg code

\subsection{Building a CFG}

@@

@@

\subsection{Interference Graph}

>>>>

\subsection{Building a Control Flow Graph}

@@

\begin{minted}[linenos,bgcolor=LightGray]{ocaml}
let graph ((head, tail) : Ll.cfg) : G.V.t array * G.t =
  let insns = flatten (head, tail) |> List.mapi (fun i n -> (i, n)) in
  let verts = Array.init (List.length insns) G.V.create in
  let addbl t = function i, Label l -> S.ST.add l verts.(i + 1) t | _ -> t in
  let blocks = List.fold_left addbl S.ST.empty insns in
  let g = G.create () in
  Array.iter (G.add_vertex g) verts;
  let addterm i = function
    | Ll.Ret _ | Unreachable -> ()
    | Br lbl -> G.add_edge g verts.(i) (S.ST.find lbl blocks)
    | Cbr (_, l1, l2) ->
        G.add_edge g verts.(i) (S.ST.find l1 blocks);
        G.add_edge g verts.(i) (S.ST.find l2 blocks)
    | Switch (_, _, _, lbls) ->
        let vert l = S.ST.find l blocks in
        List.map snd lbls |> List.map vert |> List.iter (G.add_edge g verts.(i))
  in
  let addedges = function
    | _, Label _ -> ()
    | i, Insn _ -> G.add_edge g verts.(i) verts.(i + 1)
    | i, Term term -> addterm i term
  in
  List.iter addedges insns;
  (verts, g)
\end{minted}

@@

\subsection{Building an Interference Graph}
